---
title: "Labweek3:binomialregression"
author: "Meghan Roberts"
date: "2023-01-26"
output: html_document
---

```{r setup, echo=TRUE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE)

library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(GGally)
library(jtools)
library(AICcmodavg)
```

#Pseodocode

* Examine data (plots, data, summary stats)
* Identify a question 
* Wrangle the data (if necessary)
* Identify some candidate models
* Select among candidate models using AIC/BIC
* Select among candidate models using k-fold cross validation
* Select among candidate models using area under Receiver Operating Characteristic Curve


```{r}
GGally::ggpairs(penguins %>% select(species, bill_length_mm:sex), 
                aes(color=species)) 
#drops some variables we are not as interested in
#with the key coloring by species
```

```{r}
#chinstrap and adelie are most similar
class(penguins$species)
levels(penguins$species)

adelie_chinstrap <- penguins %>%
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species=fct_drop(species)) %>% 
  select(-year) %>% 
  drop_na()
  #drop any levels that no longer exist in it (aka Gentoo)
# %in% looks for and A or a C, == means a match in order
# essentially, use %in% instead of ==
levels(adelie_chinstrap$species)
```

#Let's look at trend across variabes
```{r}
#body mass vs lipper length
ggplot(data=adelie_chinstrap, aes(x=body_mass_g, y=flipper_length_mm))+
  geom_point(aes(color=sex, shape=island))+
  facet_wrap(~ species)
# facet_wrap is separating the plots by species

#body mass vs bill length
ggplot(data = adelie_chinstrap, aes(x=body_mass_g, y=bill_length_mm))+
  geom_point(aes(color=sex, shape=island))+
  facet_wrap(~ species)
```

## Let's do some binary logistic regression

```{r}
f1 <- species ~ body_mass_g+flipper_length_mm+sex #formula 1
ad_chin_blr1 <-glm(data=adelie_chinstrap, formula = f1, family = "binomial")
ad_chin_blr1
summary(ad_chin_blr1)

blr1_tidy <- tidy(ad_chin_blr1) #makes a nice dataframe
```



